---
title: "DDP Final"
author: "Sean"
date: "11/1/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Agenda

Welcome!  Below is our agenda

- Page 1 (Was the title page before this)
- Page 2 (This page!)
- Page 3 (A brief (extremely brief) description of the project)
- Page 4 (Explanation of the Inputs/Outputs)
- Page 5 (SSA Information and Farewell)

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(leaflet)
library(htmltools)
library(plotly)
```

## What I have Made

This is a retirement calculator.  Below is the link to the calculator.

[https://s-sq.shinyapps.io/test/](https://s-sq.shinyapps.io/test/)

This tool is designed to allow a married couple to plan their retirement based on their pensions, social security, and principal at retirement


## Inputs

Inputs:

- Starting Principal (Money in the Bank)
- Expected Interest (How much we're making on it)
- First Person's Retirement Year and Month
- Second Person's Retirement Year and Month
- Initial Monthly Withdrawal Amount, Year, and Month
- Second Monthly Withdrawal Amount, Year, and Month (Replaces the Initial)

Outputs:

- Top Chart: Blue Line - The Total Amount Paid Out through Time
- Top Chart: Green Line - The Amount of Principal Remaining through Time
- Bottom Chart: Monthly Payouts


## Thanks For Coming.

Here's some code showing the SSA payout information.
```{r}
library(ggplot2)
library(plotly)
df <- read.csv('Age.csv')
p <- ggplot(df, aes(x = Months_Early, y = Payout)) + geom_path(color = 'blue', size = '2') + labs(title = 'Retirement Payout', x = 'Months from First Possible Withdrawal', y = 'Percentage of Payout')

ggplotly(p)
```

It's been fun!  I thought this class was actually pretty useful.  See you around!

